MP MetaAnalysis

### 2018-05-30 Paper_Analyses.Rmd
created "Paper_Analyses"
Paper_Analyses better reflects the order of analyses in the manuscript,
making writing easier.

@@

The table below shows based on which data we calculated effect sizes.

@@

We also have different ways of comparison of the time-course data, as the next table shows.
```{r DescriptivesComparison, echo = FALSE}
db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
 "post-naming phase compared with chance (=50%)",
ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))

@@

This is a summary of the type of distractor used in an experiment

@@

This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment

@@

## Analysis time window

@@

Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.

@@

## Early Ages
Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity

@@

## Correct object identification effect

@@

summary(rma_correct_age)

@@

## Mispronunciation object identification effect

@@

## Mispronunciation effect
```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

@@

@@

### Language effect

Followup: Per condition (correct or MP) the interaction with age

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)
```

### Type of distractor

```{r DistractorTypeAge}

@@

## Type of Distractor with age
```{r DistractorTypeAge}

@@

#### Subset to same age range

```{r DistractorTypeAge}

### Distractor Overlap

## Number of features

### Interaction with condition

## MP location

## MP type: Vowel, consonant, or tone?

### Interaction with condition
```{r MPtypeCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

### Interaction with language
```{r MPtypeLanguage}
#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
#                type_feature == "tone")

### Interaction with condition and language
```{r MPtypeLanguageCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
                #type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

```
## Correlation MP effect and vocabulary

@@

# Plotting
```{r PlotAPATheme}
#Themes and plot
apatheme=theme_bw()+
  theme(#panel.grid.major=element_blank(),
    #panel.grid.minor=element_blank(),
    #panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

```
## Mispronunciation Effect by Age (color)
```{r PlotMPEffect}

```
## Mispronunciation Effect by Age (bw)
```{r PlotMPEffect_BW}

@@

## MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect}

@@

## Language Family by MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect_Lang}

p <- ggplot(dat, aes(type_feature, g_calc, color = type_feature)) + 
  geom_boxplot() + 
  facet_grid(lang_family~condition_label)+
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Language Family") + 
  ylab("Effect size Hedges' g")
p

@@

## Number of Features
```{r PlotFeatEffect}

#dat_f <- subset(dat, n_feature == "0" | n_feature == "1" | n_feature == "2" | n_feature == "3")

p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = n_feature)) + 
  geom_point(aes(size = weights_g, shape = n_feature),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

@@

## Position of Mispronunciation
```{r PlotPositionEffect}

dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
                mispron_location == "offset")

@@

## Distractor Familiarity
```{r PlotDistFamEffect}

@@

## Distractor Familiarity (w/o age)
```{r PlotDistFamEffect_NoAge}

@@

## Distractor Familiarity (w/o age, subset to age range)
```{r PlotDistFamEffect_NoAge_AgeMatch}

@@

## Overlap between distractor and target

@@

## Language Family
```{r PlotLanguageEffect}

>>>>

# Plotting defaults

```{r PlotAPATheme}
#Themes and plot
apatheme=theme_bw()+
  theme(panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.border=element_blank(),
    axis.line=element_line(),
    text=element_text(family='Times', size=25))

@@

## Type of data on which we calculated effect sizes
The table below shows based on which data we calculated effect sizes.

@@

## Type of comparison of the time-course data calculated
We also have different ways of comparison of the time-course data, as the next table shows.

```{r DescriptivesComparison, echo = FALSE}
db_ET_correct$within_measure_descriptive <- ifelse(db_ET_correct$within_measure == "post",
 "post-naming phase compared with chance (=50%)",
ifelse(db_ET_correct$within_measure == "pre_post", "post-naming compared to pre-naming phase", "post-pre difference score compared with chance (=0)"))

@@

## Type of distractor
This is a summary of the type of distractor used in an experiment

@@

## Whether word was pronounced both correctly as well as mispronounced
This is a summary of whether an experiment had both correct and mispronounced versions of the word in the experiment

@@

## Size of analysis time window

@@

## Duration of post naming window
Next we look at duration (in seconds) of the post naming window, here,too, we see a lot of heterogeneity.

@@

## Mispronunciation Sensitivity in the youngest ages
Even the youngest ages in the database (less than 1 year) show mispronunciation sensitivity

@@

## Main Mispronunciation Sensitivity Effects

### Correct object identification effect

@@

#kable(round(coef(summary(rma_correct)), 2))

@@

### Mispronunciation object identification effect

@@

### Mispronunciation Sensitivity effect

```{r MPEffect}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

@@

## Main Mispronunciation Sensitivity Effects with Age Moderators

### Correct object identification effect with age moderator

```{r MAcorrect_age}

summary(rma_correct_age)
#kable(round(coef(summary(rma_correct_age)), 2))

### Mispronunciation object identification effect with age moderator

```{r MAMP_age}

### Mispronunciation Sensitivity effect with age moderator

```{r MPEffect_age}
db_ET_correct$condition <- 1
db_ET_MP$condition <- 0

@@

### Plot Mispronunciation Effect by Age (color)

```{r PlotMPEffect}

@@

### Plot Mispronunciation Effect by Age (bw)

```{r PlotMPEffect_BW}

@@

## Correlation MP effect and Vocabulary

@@

## Number of features
Size of mispronunciation, measured in features changed

@@

### Number of features with condition moderator

### Number of features with age moderator

```{r NFeatures_age}

### Number of features with condition and age moderators

```{r NFeaturesCondition_age}

### Plot number of Features

```{r PlotFeatEffect}

dat_f$feat_cat <- ifelse(dat_f$n_feature == 1, "one",
                         ifelse(dat_f$n_feature == 2, "two",
                                ifelse(dat_f$n_feature == 3, "three",
                                       ifelse(dat_f$n_feature == 0, "correct", "none"))))

dat_f <- subset(dat_f, feat_cat != "none")

p <- ggplot(dat_f, aes(mean_age_1/30.44, g_calc, color = feat_cat)) + 
  geom_point(aes(size = weights_g, shape = feat_cat),show.legend=FALSE) + 
  #facet_grid(.~type_feature)+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Age in months") + 
  ylab("Effect size Hedges' g")
p

## Type of MP: Vowel, consonant, or tone

### Type of MP: Vowel, consonant, or tone with age moderator

```{r MPtype_age}
db_MP_type <- subset(db_ET_MP, type_feature == "consonant" | type_feature == "vowel" )

### Type of MP: Vowel, consonant, or tone with condition moderator

```{r MPtypeCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

### Type of MP: Vowel, consonant, or tone with age and condition moderator

```{r MPtypeCondition_age}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
                type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

### Type of MP with language family moderator

```{r MPtypeLanguage}
#dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel" |
#                type_feature == "tone")

### Type of MP with language family and condition moderators

```{r MPtypeLanguageCondition}
dat_type <- subset(dat, type_feature == "consonant" | type_feature == "vowel")# |
                #type_feature == "tone")
dat_type$type_feature <- as.factor(ifelse(dat_type$condition == 1, "none", dat_type$type_feature))

### Plot MP type: Consonant, Vowel, or Tone?

```{r PlotCVEffect}

@@

### Plot Language Family by MP type: Consonant, Vowel, or Tone?
```{r PlotCVEffect_Lang}

p <- ggplot(dat_type_sub, aes(type_feature, g_calc, color = type_feature)) + 
  geom_boxplot() + 
  facet_grid(lang_family~condition_label)+
  #geom_line(y= 0, linetype="dotted") + 
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  theme(text = element_text(size=16)) + 
  xlab("Language Family") + 
  ylab("Effect size Hedges' g")
p

@@

## Distractor Familiarity (familiary, unfamiliar)

```{r DistractorType}

rma_Distractor <- rma.mv(g_calc, g_var_calc, mods = ~as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

@@

### Distractor Familiarity with condition moderator

```{r DistractorTypeCondition}

@@

### Distractor Familiarity with age moderator
```{r DistractorTypeAge}

rma_DistractorAge <- rma.mv(g_calc, g_var_calc, mods = ~age.C*as.factor(object_pair), data = dat, random = ~ collapse | short_cite)

### Distractor Familiarity with age and condition moderators
```{r DistractorTypeConditionAge}

### Distractor Familiarity with age moderator, subset to same age range

```{r DistractorTypeAgeRangeSubset}

### Plot Distractor Familiarity

```{r PlotDistFamEffect}

@@

### Plot Distractor Familiarity (w/o age)

```{r PlotDistFamEffect_NoAge}

@@

### Plot Distractor Familiarity (w/o age, subset to age range)

```{r PlotDistFamEffect_NoAge_AgeMatch}

@@

## Position of Mispronunciation (onset, medial)

### Position of Mispronunciation with age moderator

```{r Location_age}
#table(db_ET_MP$mispron_location)

### Position of Mispronunciation with condition moderator

```{r Location_condition}
#table(db_ET_MP$mispron_location)

rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition, data = db_ET_MPl, random = ~collapse | short_cite)

summary(rma_LocationCondition)
```

### Position of Mispronunciation with age and condition moderators

```{r Location_condition_age}
#table(db_ET_MP$mispron_location)

rma_LocationCondition <- rma.mv(g_calc, g_var_calc, mods = ~mispron_location*condition*age.C, data = db_ET_MPl, random = ~collapse | short_cite)

summary(rma_LocationCondition)
```

### Plot Position of Mispronunciation
```{r PlotPositionEffect}

#dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial" |
#                mispron_location == "offset")

dat.p <- subset(dat, mispron_location == "onset" | mispron_location == "medial")

## Distractor Overlap

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

### Distractor Overlap with age moderator

```{r DistractorOverlap_age}

### Distractor Overlap with condition moderator

```{r DistractorOverlap_condition}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

### Distractor Overlap with age and condition moderators

```{r DistractorOverlap_age_condition}

rma_DistractorOverlap <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*distractor_overlap, data = db_ET_MP, random = ~ collapse | short_cite)

### Plot Distractor Overlap

@@

## Language effect

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

### Language effect with age moderator

```{r LanguageEffectAnalyses_age}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

### Language effect with condition moderator

```{r LanguageEffectAnalyses_condition}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

### Language effect with age and condition moderators

```{r LanguageEffectAnalyses_condition_age}
dat$condition_label = ifelse(dat$condition==1, "Correct", "Misp")

rma_lang_interaction <- rma.mv(g_calc, g_var_calc, mods = ~age.C*condition*lang_family, data = dat, random = ~ collapse | short_cite)
summary(rma_lang_interaction)

### Plot Language Effect
```{r PlotLanguageEffect}
